Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2021-01-07 GWLDCII.tex
Zee's final comments

The Amplituhedron and the Wilson loop diagrams describe the scattering amplitudes from the same physical theory, but the Amplituhedron only captures the on-shell portion while the Wilson loop diagrams capture arbitrary kinematics.   Both are related to positroids, and in this way they have similar combinatorics, but, these combinatorial objects manifest themselves differently in the two cases.  For instance, square moves and merge-expand moves on the plabic graph give different graphical representations, hence parametrizations, of the same positroid cell in the Amplituhedron case.  On the other hand, we show in our companion paper \cite{generalcombinatoricsI}, retriangulations of polygon dissections associated to Wilson loop diagrams give all the Wilson loop diagrams associated to the same positroid cell.  Each distinct Wilson loop diagram associated to the same positroid cell gives a different parametrization \cite{WLDdim}. % Despite their common representation as positroids,a direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams is not known.  The geometric spaces in the two situations have different dimensions, as we will discuss further below, and examples show\cite{HeslopSteward} that they do not relate by a coordinate projection or boundary map or other straightforward function.
The deeper combinatorial and geometric connection between the Amplituhedron and the Wilson loop diagrams, which physics tells us should exist, remains to be uncovered in future work.

>>>>

The Amplituhedron and the Wilson loop diagrams describe the scattering amplitudes from the same physical theory, but the Amplituhedron only captures the on shell portion while the Wilson loop diagrams capture arbitrary kinematics.   Both are related to positroids, and in this way they have similar combinatorics, but, these combinatorial objects manifest themselves differently in the two cases.  For instance, square moves and merge-expand moves on the plabic graph give different graphical representations, hence parametrizations, of the same positroid cell in the Amplituhedron case.  On the other hand, as we show in our companion paper \cite{generalcombinatoricsI}, retriangulations of polygon dissections associated to Wilson loop diagrams give all the Wilson loop diagrams associated to the same positroid cell.  Each distinct Wilson loop diagram associated to the same positroid cell gives a different parametrization \cite{WLDdim}. % Despite their common representation as positroids,a direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams is not known.  The geometric spaces in the two situations have different dimensions, as we will discuss further below, and examples show\cite{HeslopSteward} that they do not relate by a coordinate projection or boundary map or other straightforward function.
The deeper combinatorial and geometric connection between the Amplituhedron and the Wilson loop diagrams, which physics tells us should exist, remains to be uncovered in future work.
